---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# VacationApp

<!-- badges: start -->
<!-- badges: end -->

The goal of VacationApp is to provide information to the user about the destination they are wishing to travel to. This package will display information about the route directions and the forecasted weather of their destination of interest

## Installation

You can install the released version of VacationApp from [CRAN](https://CRAN.R-project.org) with:

``` r
install.packages("VacationApp")
```

```{r include = FALSE}
library(VacationApp)
```

## Directions Function
The directions() function will provide directions on how to arrive to the designated route of choice. This function takes the following inputs: from, to. The parameter *from* will take in a string specifying the starting location of their travel route. The parameter *to* will take in a string specifying the final destination of their travel route. Both parameters will need to be in the format "Street Address, City, State."
## Weather Function
